---
title: "Week 10 Problem Set"
author: "Maya Komakhidze"
format: html
execute:
  echo: true
  warning: true
  message: true
---

# Generate dataset reproducibly
set.seed(1903)
subject_id <- 1:40
rt <- round(rnorm(40, mean = 520, sd = 120))
rt[sample(1:40, 2)] <- NA
congruent <- sample(c(TRUE, FALSE), 40, replace = TRUE)
condition <- sample(c("control", "incongruent"), 40, replace = TRUE)
experiment_data <- data.frame(subject_id, rt, congruent, condition)

# Save for reuse in later tasks
saveRDS(experiment_data, file = "data/raw/experiment_data.rds")

rm(list = ls())

#### Q1: Load and Inspect Data ------------------------------------

```{r}
## Load the saved dataset
experiment_data <- readRDS("../data/raw/experiment_data.rds")

## Take a quick look at the first few rows
head(experiment_data)

## Check the structure of the dataset
str(experiment_data)

```

#### Q2: Functions ------------------------------------------------

```{r}
## Generate one or more random numbers between min and max (defaults: one number between 1–10)
getRandomNumber <- function(min = 1, max = 10, number = 1) {
  sample(min:max, number)
}
```

```{r}
## Classify reaction times into "Fast", "Slow", or "Unknown" (default threshold = 500ms)
rt_class <- function(rt, threshold) {
  if (!is.numeric(threshold) || length(threshold) != 1) {
    stop("Error: 'threshold' must be a single numeric value.")
  }
  if (!is.numeric(rt)) {
    stop("Error: 'rt' must be numeric.")
  }
  category <- ifelse(
  is.na(rt), "unknown",
  ifelse(rt<500, "fast", "slow")
  )
  return(category)
}
rt <- c(1, 501, 100, NA)

rt_class(rt, 500)  

```

### Q3: Loops vs. Vectorization -------------------------
```{r}
# Creating an age column with a for loop
experiment_data$age <- NA
for (i in 1:nrow(experiment_data)) {
  experiment_data$age[i] <- getRandomNumber(18,65, 1)
}
head(experiment_data)

# Creating the column with vectorization
experiment_data$age <- sample(18:65, size=nrow(experiment_data), 
                              replace = TRUE)
head(experiment_data)
```
### Q4: Control Structures on Data Frames ---------------------------
```{r}
# Creating an RT categorization using for loop
experiment_data$rt_category <- NA
for (i in 1:nrow(experiment_data)) {
  rt_class(experiment_data$rt[i],500) -> experiment_data$rt_category[i]
}

# Creating an RT categorization using vectorization
experiment_data$rt_category_vec <- NA
experiment_data$rt_category_vec <- rt_class(experiment_data$rt, 500)

# Comparing the two
table(loop = experiment_data$rt_category,
      vec  = experiment_data$rt_category_vec,
      useNA = "ifany")
```
### Q5: Debugging Functions -----------------------------
```{r}
## Create Buggy Function
threshold <- 500

flag_fast <- function(rt_vector, threshold=500) {
  rt_vector < threshold
}
flag_fast(experiment_data$rt)
rm(threshold)

```
### Q6: Debugging Tools in Action -----------------------------
```{r}
subject_means <- tapply(experiment_data$rt,
                        experiment_data$condition,
                        mean, na.rm=TRUE)
print(paste("Mean for control:", subject_means["control"]))
print(paste("Mean for incongruent:", subject_means["incongruent"]))
# How many NAs overall?
sum(is.na(experiment_data$rt))

# How many NAs by condition?
tapply(is.na(experiment_data$rt), experiment_data$condition, sum)

# Optional: quick sanity checks
summary(experiment_data$rt)
with(experiment_data, table(condition, is.na(rt)))
```

### Q7: Using AI for Debugging or Refactoring --------------------
AI was useful in diagnosing the key issue - that my code didn't include
a range for the for loop function, it only included a single value because
nrow() produces the total number of rows.

### Q8: Saving and Reloading Objects -----------------------------
```{r}
write.csv(experiment_data, file="/Users/mayak/Desktop/psy1903/web/week10_taskset/data/cleaned/experiment_data.csv")
saveRDS(experiment_data, file="/Users/mayak/Desktop/psy1903/web/week10_taskset/data/cleaned/experiment_data.rds")
save(experiment_data, subject_means, file = "objects.RData")
rm(list = ls())
```
