---
title: "ai-factor"
format: html
---
# Issues I found in the files
Beyond the bug fixes that prevented the code from running, I made the following changes in he summarize behavior file:
1. Removed the below if condition because the function already checks if a variable is logical.
```{r}
#if (!is.logical(data$correct)) { 
#  data$correct <- normalize_logical(data$correct)
#  } 
```

2. For filtering out trials where RT was outside of the threshold range I changed the indexing based on column numbers with named columns
3. I changed hard-coded values to the variables specified in the function


# AI suggestions on unmodified files:
## 1. Use vectorized operations instead of small loops
## 2. Inside loops that build participant-level summaries, create an empty list or data frame and fill by index rather than repeated rbind()
This suggestion relates to the function
```{r}
#for (i in seq_along(files)) {
#    file_name <- files[i]
#    rows[[i]] <- import_and_process(file_name)
#  }

#  out  <- do.call(rbind, rows)
```

## 3. Replace sapply() with vapply() for type stability and speed
If any block is empty, sapply() returns weird shapes. vapply() is safer and faster:

```{r}
# means <- sapply(split(df$RT, df$block), mean)

# means <- vapply(split(df$RT, df$block), mean, numeric(1))
```

# AI suggestions on refactored files:

## 1. Too much logic is spread across multiple scripts with partial duplication

Examples:

import_and_process.R performs trial filtering and summary calculations

calculate_iat_dscore.R performs its own filtering and standardization

summarize_behavior.R has yet another set of filtering + mean operations

This means that “what counts as a valid trial” or “how accuracy is calculated” is encoded in three places.

Improvement
Create one central task-processing module with reusable helpers:
```{r}
# process_trials()
# block_summary()
# trim_rt()
# compute_accuracy()
```
Then every script calls the same utilities instead of implementing its own version.

## 2. summarize_behavior.R and build_participant_wide.R these two scripts show the most obvious remaining redundancy.

Improvement opportunities:
A. They duplicate summary logic from the main import script

General pattern:

compute mean RTs
compute accuracy
assemble a summary frame

But these exist in two scripts with slightly different implementations.

Centralize into:

summarize_trials(df)

Then every script uses the same function, eliminating drift.
## 3. Validate all required columns early and simply

```{r}
# required <- c("block","RT","correct")
# missing <- setdiff(required, names(df))

# if (length(missing) > 0)
#    stop("Missing columns in IAT data: ", paste(missing, collapse=", "))
```

# Comparison between AI and me
AI also suggested replacing for loops with vectorized operations but other suggestions were more high-level - like concentrating functions in the same file and reducing the number of temporary dataframes to increase efficiency.